```{r}

setwd("C:/Users/Nupur Rathi/Desktop/Assignments PGBABi/Projects/Cart and Random Forest Project")
#Reading data
library(readxl)
bankData<-read_excel("Thera Bank-Data Set.xlsx",2)

```

#Converting type of variables
```{r}
bankData$Education<-as.factor(bankData$Education)
bankData$`Personal Loan`<-as.factor(bankData$`Personal Loan`)
bankData$`Securities Account`<-as.factor(bankData$`Securities Account`)
bankData$`CD Account`<-as.factor(bankData$`CD Account`)
bankData$Online<-as.factor(bankData$Online)
bankData$CreditCard<-as.factor(bankData$CreditCard)
bankData$`Family members`<-as.factor(bankData$`Family members`)
bankData$`ZIP Code`<-as.factor(bankData$`ZIP Code`)

str(bankData)
#check for any duplicate rows
any(duplicated(bankData))

#change name of colmns : Different ways to  change column name
# we can trim all col names
names(bankData)<-gsub("\\s","_",names(bankData)) #subsitutes space by underscore
colnames(bankData)
```


```{r}

names(bankData)
#Data Cleaning 
"
1.Experience in years : has negative values.
2.Missing values in FamilyMembers.
3.Remove Unnecessary variables which cant help us in prediction like 'Id'
4.Income_(in_K_per_month has outliers.
5.average spending on credit card has many outliers:CCAvg

"
library(dplyr)

bankData %>%
  filter(is.na(bankData$Family_members))

bankData %>%
  filter(bankData$`Experience_(in_years)`<0)
#Conclude: There are 52 rows where experience is negative : Exp cant be negative # so we will mutate as abs value of exp : considering it to be typing err

bankData$`Experience_(in_years)`=abs(bankData$`Experience_(in_years)`)
bankData<-bankData[,-c(1,5)]


```
```{r}
"
For Missing values in FamilyMembers.lets build a model to predict the family members for given data" 


"For now , just mutate it as 1 : considering they are single person"
bankData[is.na(bankData$Family_members),"Family_members"]<- 1

#check if missing value got replaced.
colSums(is.na(bankData))

```


#Splitting the data into test and traindata
```{r}

library(caTools)

set.seed(127)

split=sample.split(bankData$Personal_Loan ,SplitRatio = 0.7)
head(bankData)
trData<-subset(bankData,split==TRUE)
tstData<-subset(bankData,split==FALSE)

#Check if the proportions of levels of PersonalLoan is same in test and train data to avoid baising
prop.table(table(trData$Personal_Loan))
prop.table(table(tstData$Personal_Loan))
```



#Step1: Trying to find best mtry by gridsearch
```{r}
#finding mtry
library(caret)
metric1="Accuracy"
tunegrid1 <- expand.grid(.mtry=c(1:12))
control=trainControl(search = "grid")
rf_gridsearch<-train(Personal_Loan~., data = trData, method ="rf",metric= metric1, tuneGrid =tunegrid1,trControl=control,ntree=500)
print(rf_gridsearch)
plot(rf_gridsearch,metric="Accuracy")
plot(rf_gridsearch,metric="Kappa")
```


```{r}
library(randomForest)
set.seed(127)
trData$predict.class=NULL
trData$predict.score=NULL
tstData$predict.class=NULL
tstData$predict.score=NULL
attach(trData)
rf2<-randomForest(Personal_Loan~., data=trData,ntree=500,mtry=4,importance=TRUE)
rf2
```

#For Bringing down the false negative: we changed cutoff to 70:30
```{r}

head(trData)
set.seed(420)
library(randomForest)
rf3<-randomForest(Personal_Loan ~ ., data=trData,ntree=500,mtry=4,importance=TRUE,cutoff=c(0.7,0.3))
rf3

```


#Plot Random Forest Tree
```{r}
require(randomForest)
k <- 100
getTree(randomForest(Personal_Loan ~ ., data=trData,ntree=500,mtry=4,importance=TRUE,cutoff=c(0.7,0.3)), k, labelVar = TRUE)

```







#Prediction for train data
```{r}
trData$predict.class=NULL
trData$predict.score=NULL

trData$predicted.class<-predict(rf3,trData,type="class")
trData$predicted.score<-predict(rf3,trData)

cfMatrix1<-table(trData$Personal_Loan,trData$predicted.class)
trueNegative<-cfMatrix1[1,1]
falsePositive<-cfMatrix1[1,2]
falseNegative<-cfMatrix1[2,1]
truePositive<-cfMatrix1[2,2]

cfMatrix1
```


#Performance Measure for train Data

```{r}
sensetivityrf_tr=truePositive/(truePositive+falseNegative)
sprintf("Senstivity: %s", sensetivityrf_tr)
specificityrf_tr=trueNegative/(trueNegative+falsePositive)
sprintf("Specificity: %s", specificityrf_tr)
accuracyrf_tr=(truePositive+trueNegative)/(truePositive+trueNegative+falsePositive+falseNegative)
sprintf("Accuracy: %s", accuracyrf_tr)
```

#Prediction for train Data

```{r}
tstData$predicted.class<-NULL
tstData$predicted.score=NULL
head(tstData)
tstData$predicted.class<-predict(rf3,tstData,type="class")
tstData$predicted.score<-predict(rf3,tstData)
cfMatrix1_tst<-table(tstData$Personal_Loan,tstData$predicted.class)
trueNegative1_tst<-cfMatrix1_tst[1,1]
falsePositive1_tst<-cfMatrix1_tst[1,2]
falseNegative1_tst<-cfMatrix1_tst[2,1]
truePositive1_tst<-cfMatrix1_tst[2,2]
cfMatrix1_tst
```





#Performance Measure for test Data

```{r}
sensetivityrf_test=truePositive1_tst/(truePositive1_tst+falseNegative1_tst)
sprintf("Senstivity: %s", sensetivityrf_test)
specificityrf_test=trueNegative1_tst/(trueNegative1_tst+falsePositive1_tst)
sprintf("Specificity: %s", specificityrf_test)
accuracyrf_test=(truePositive1_tst+trueNegative1_tst)/(truePositive1_tst+trueNegative1_tst+falsePositive1_tst+falseNegative1_tst)
sprintf("Accuracy: %s", accuracyrf_test)
```
#Model Performance of Test and Train
```{r}
df_results_train = data.frame(accuracyrf_tr, sensetivityrf_tr, specificityrf_tr)
names(df_results_train) = c("ACC", "SENS", "SPEC")
df_results_test = data.frame(accuracyrf_test, sensetivityrf_test, specificityrf_test)
names(df_results_test) = c("ACC", "SENS", "SPEC")

?rbind
df_fin =rbind(df_results_train, df_results_test)
row.names(df_fin) = c('tree_full_train', 'tree_full_test')
df_fin
```


#Calculating AUC with best model(rf3)

```{r}

trData$predicted.class=predict(rf3,trData,type="class")
trData$predicted.score=predict(rf3,trData,type="prob")
tstData$predicted.score=predict(rf3,tstData,type="prob")
```


```{r}
library(pROC)
roc_obj_rf1 = roc(trData$Personal_Loan, trData$predicted.score[,2])
plot(roc_obj_rf1, print.auc = T)
roc_obj_rf2 = roc(tstData$Personal_Loan, tstData$predicted.score[,2])
plot(roc_obj_rf2, print.auc = T)
```


